Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-08 paper.tex
minor tweaks

Informal comparison of results from the VISION and Cyclus simulators when
running equivalent scenarios revealed some surprising discrepancies.  One of
the most apparent was a large difference in separated Pu levels between the
two simulators --- something that some in the DOE and nuclear community are
very sensitive to.  For one particular scenario, the Cyclus results also
showed no fuel shortages for reactors, while the VISION results indicated
noticeable shortages.  This observation prompted a closer investigation to
determine if the differences were caused by mistakes in simulator input, bugs
in the simulator(s), or differing modeling choices between the simulators.
This investigation eventually developed into this work which shows important
effects of some modeling choices that are operative in many fuel cycle
simulators.

@@

%% response to technical comment 1.
These four cases span a spectrum of fidelity with one end being more realistic
(i.e., smaller time steps, individual facilities) and the other being more
appropriate for scoping studies (i.e.,  larger time steps, fleet facilities).
Conducting this analysis involved developing some additional capability
in/around Cyclus.  Three primary pieces to the methodology are:

@@

Because the standard package of archetypes included with Cyclus does not
include a fleet-based reactor model, one was necessarily developed. A
simulation scenario was created that is roughly based on prior and ongoing
work in the Department of Energy (DOE) fuel cycle options campaign \cite{hoffman-eg23-2016}.  A few
phenomena related to the different modeling choices in each of the four cases
are identified and used as a basis for comparison.  These are
described in more detail in the following sections.

>>>>

Informal comparison of results from the VISION and Cyclus simulators when
running equivalent scenarios revealed some surprising discrepancies.  One of
the most apparent was a large difference in separated Pu levels between the
two simulators --- something that some in the DOE and nuclear community are
very sensitive to.  For one particular scenario, the Cyclus results also
showed no fuel shortages for reactors, while the VISION results indicated
noticeable shortages.  This observation prompted a closer investigation to
determine if the differences were caused by mistakes in simulator input, bugs
in the simulator(s), or different (yet still reasonable) modeling choices of the simulators.
This investigation eventually developed into this work which shows important
effects of that are operative in many fuel cycle simulators.

@@

%% response to technical comment 1.
\noindent
These four cases span a spectrum of fidelity with one end being more realistic
(i.e., smaller time steps, individual facilities) and the other being more
appropriate for scoping studies (i.e.,  larger time steps, fleet facilities).
Conducting this analysis involved developing some additional capability
in/around Cyclus.  Three primary pieces to the methodology are:

@@

\noindent
Because the standard package of archetypes included with Cyclus does not
include a fleet-based reactor model, one was necessarily developed. A
simulation scenario was created that is roughly based on prior and ongoing
work in the Department of Energy (DOE) fuel cycle options campaign \cite{hoffman-eg23-2016}.  A few
phenomena related to the different modeling choices in each of the four cases
are identified and used as a basis for comparison.  These are
described in more detail in the following sections.
